\morus: Biases in the Stream

### 2018-05-10 morusAC_04_Mini_trails.tex
minor fix

To confirm that our analysis is correct, we ran experiments on an implementation of \MiniMORUS[1280] and \MiniMORUS[640]. In both cases, we measured the correlation of two halves $\chi_1$ and $\chi_2$ of the full trail, as well as the correlation of the full trail itself (denoted by $\chi$). Results are displayed on \Cref{tab:miniapproximations}.
While our analysis from the previous section predicts a correlation of $2^{-16}$, experiments indicate a slightly better empirical correlation of $2^{-15.5}$ for \MORUS[640]. The discrepancy of $2^{-0.5}$ probably arises from the fact that register bits across different steps are not completely independent.

In order to preserve anonymity, our implementation is attached to the submission as auxiliary material. In the full version of this paper, a link will be provided instead.

>>>>

To confirm that our analysis is correct, we ran experiments on an implementation of \MiniMORUS[1280] and \MiniMORUS[640]. In both cases, we measured the correlation of two halves $\chi_1$ and $\chi_2$ of the full trail, as well as the correlation of the full trail itself (denoted by $\chi$). Results are displayed on \Cref{tab:miniapproximations}.
While our analysis from the previous section predicts a correlation of $2^{-16}$, experiments indicate a slightly better empirical correlation of $2^{-15.5}$ for \MiniMORUS[640]. The discrepancy of $2^{-0.5}$ probably arises from the fact that register bits across different steps are not completely independent.

In order to preserve anonymity, our implementation is attached to the submission as auxiliary material. In the full version of this paper, a link will be provided.
